---
title: "DISCOVR SOT Analysis"
author: "Paige Norris, NREL, May 2022"
output: html_document

---

```{r, echo = FALSE, message=FALSE}
# Author: Paige Norris
# Date: May 2022
# Goal: Create interactive graphs from composition and cultivation data formatted in 
# DISCOVR_data_clean.R

# Takes user input and creates an interactive HTML with graphs pertaining to growth
# trends of specific algae strain(s) over a set period of time. Works in tandem with 
# DISCVOR_data_clean.R. 
```

```{r, echo = FALSE, message=FALSE}
library(tidyverse)
library(usethis)
library(devtools)
# USER INPUT: Enter the dates of the time period you would like to look at in form YYYY-MM-DD
start_date = "2020-05-01"
end_date = "2020-07-31"

# USER INPUT: Enter desired algae strain, needs to match file name perfectly
strain = "P.celeri"

# NOTE: THE BELOW FILE IS PULLED FROM PAIGE NORRIS'S (paigeanorris@gmail.com) GITHUB 
# DUE TO THE PRIVATE SETTING ON THE NREL-ALGAE TEAM REPO
source_url("https://raw.githubusercontent.com/paiyge/DISCOVR/main/cleaning")
```

### All variables plotted against time in days

```{r, echo = FALSE, message=FALSE}
library(ggplot2)
plot1 <- ggplot(all_variable) +
           aes(x = DateTime, y = Value, fill = Variable, colour = PondID) +
           geom_line(size = 0.5) +
           theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
           scale_fill_hue(direction = 1) +
           scale_color_hue(direction = 1) +
           labs(x = "DateTime", y = "Value", fill = "Variable", color = "PondID") +
           theme_minimal()
```

```{r, echo = FALSE, message=FALSE}
library(plotly)
ggplotly(plot1)

```

### All variables plotted against time in days, by pond

```{r, echo = FALSE, message=FALSE}
library(ggplot2)
plot2 <- ggplot(all_variable) +
           aes(x = DateTime, y = Value, fill = Variable) +
           geom_line(size = 0.5, colour = "#112446") +
           scale_fill_hue(direction = 1) +
           labs(x = "DateTime", y = "Value", fill = "Variable") +
           theme_minimal() +
           facet_wrap(vars(PondID))
```

```{r, echo = FALSE, message=FALSE}
library(plotly)
ggplotly(plot2)

```

### All variables plotted against time in days, by variable

```{r, echo = FALSE, message=FALSE}
library(ggplot2)
### Facets by ponds, color = variable
plot3 <- ggplot(all_variable) +
           aes(x = DateTime, y = Value, colour = Variable) +
           geom_line(size = 0.5) +
           scale_color_hue(direction = 1) +
           labs(x = "DateTime", y = "Value", color = "PondID") +
           theme_minimal() +
           facet_wrap(vars(PondID))
```

```{r, echo = FALSE, message=FALSE}
library(plotly)
ggplotly(plot3)

```

### All variables plotted against time in days, by pond

```{r, echo = FALSE, message=FALSE}
library(ggplot2)
plot4 <- ggplot(all_variable) +
           aes(x = DateTime, y = Value, colour = PondID) +
           geom_line(size = 0.5) +
           scale_color_hue(direction = 1) +
           theme_minimal() +
           facet_wrap(vars(Variable), scales = "free")
```

```{r, echo = FALSE, message=FALSE}
library(plotly)
ggplotly(plot4)

```

### AFDW over time

```{r, echo = FALSE, message=FALSE}
library(ggplot2)
plot5 <- ggplotly(ggplot(strain_afdw) +
           aes(x = DateTime, y = Value, colour = PondID) +
           geom_point(shape = "circle", size = 1.5) +
           geom_line() +
           scale_color_hue(direction = 1) +
           theme_minimal() +
           facet_wrap(vars(Variable)))
```

```{r, echo = FALSE, message=FALSE}
library(plotly)
ggplotly(plot5)

```


### AFDW over time
```{r, echo = FALSE, message=FALSE}
library(ggplot2)
plot6 <- ggplotly(ggplot(strain_afdw) +
           aes(x = DateTime, y = Value, colour = PondID) +
           geom_line(size = 0.5) +
           scale_color_hue(direction = 1) +
           theme_minimal() +
           facet_wrap(vars(Variable)))
```

```{r, echo = FALSE, message=FALSE}
library(plotly)
ggplotly(plot6)

```

### AFDW with DLI over time

```{r, echo = FALSE, message=FALSE}
library(ggplot2)
plot7 <- ggplotly(ggplot(dli_afdw) +
           aes(x = DateTime, y = Value, colour = PondID) +
           geom_point() +
           geom_line(size = 0.5) +
           scale_color_hue(direction = 1) +
           theme_minimal())
```

```{r, echo = FALSE, message=FALSE}
library(plotly)
ggplotly(plot7)

```

### DLI with slope productivity

```{r, echo = FALSE, message=FALSE}
library(ggplot2)
plot8 <- ggplotly(ggplot(dli_asp) +
  aes(x = DateTime, y = Value, colour = PondID) +
  geom_line(size = 0.5) +
  scale_color_hue(direction = 1) +
  theme_minimal())
```

```{r, echo = FALSE, message=FALSE}
library(plotly)
ggplotly(plot8)

```

### AFDW vs Date facets by ponds
```{r, echo = FALSE, message=FALSE}
library(ggplot2)
plot9 <- ggplotly(ggplot(strain_data) +
           aes(x = DateTime, y = AFDW.AVE, colour = PondID) +
           geom_line(size = 0.5) +
           scale_color_hue(direction = 1) +
           theme_minimal() +
           facet_wrap(vars(PondID)))
```
           
```{r, echo = FALSE, message=FALSE}
library(plotly)
ggplotly(plot9)
```

### Growth, Composition, and DLI over time for FY 2020
```{r, echo = FALSE, message=FALSE}
library(ggplot2)
plot10 <- ggplotly(ggplot(all_variable) +
  aes(x = DateTime, y = Value, fill = Variable, colour = PondID) +
  geom_line(size = 0.5) +
  scale_fill_hue(direction = 1) +
  scale_color_hue(direction = 1) +
  labs(title = "Growth, Composition, and DLI over time for FY 2020", 
       subtitle = "AFDW, ASP, NH4, PO4", fill = "all_variable$variable") +
  theme_minimal())
```
 

```{r, echo = FALSE, message=FALSE}
library(plotly)
ggplotly(plot10)
```

### Growth, Composition, and DLI over time
```{r, echo = FALSE, message=FALSE}
library(ggplot2)
plot11 <- ggplotly(ggplot(all_variable) +
  aes(x = DateTime, y = Value, fill = Variable, colour = PondID) +
  geom_line(size = 0.5) +
  scale_fill_hue(direction = 1) +
  scale_color_hue(direction = 1) +
  labs(title = "Growth, Composition, and DLI over time for FY 2020", 
       subtitle = "AFDW, ASP, NH4, PO4", fill = "all_variable$variable") +
  theme_minimal())
```

```{r, echo = FALSE, message=FALSE}
library(plotly)
ggplotly(plot11)
```

# DLI and Slope Productivity over time
```{r, echo = FALSE, message=FALSE}
library(ggplot2)
plot12 <- ggplotly(ggplot(dli_asp) +
  aes(x = DateTime, y = Value, fill = Variable, colour = PondID) +
  geom_line(size = 0.5) +
  scale_fill_hue(direction = 1) +
  scale_color_hue(direction = 1) +
  labs(title = "Growth, Composition, and DLI over time for FY 2020", 
       subtitle = "AFDW, ASP, NH4, PO4", fill = "all_variable$variable") +
  theme_minimal())
```
  
```{r, echo = FALSE, message=FALSE}
library(plotly)
ggplotly(plot12)
```
### Slope Productivity and NH4 over time
```{r, echo = FALSE, message=FALSE}
library(ggplot2)
plot13 <- ggplotly(ggplot(asp_nh4) +
 aes(x = DateTime, y = Value, fill = Variable, colour = PondID) +
 geom_line(size = 0.5) +
 scale_fill_hue(direction = 1) +
 scale_color_hue(direction = 1) +
 labs(x = "Date", y = "Value", title = "Slope Productivity and NH4 over time") +
 theme_minimal())
```
  
```{r, echo = FALSE, message=FALSE}
library(plotly)
ggplotly(plot13)
```

```{r, echo = FALSE, message=FALSE}
library(ggplot2)
plot14 <- ggplotly(ggplot(asp_po4) +
 aes(x = DateTime, y = Value, fill = Variable, colour = PondID) +
 geom_line(size = 0.5) +
 scale_fill_hue(direction = 1) +
 scale_color_hue(direction = 1) +
 labs(x = "Date", y = "Value", title = "Slope productivity and PO4 over time") +
 theme_minimal())
```
  
```{r, echo = FALSE, message=FALSE}
library(plotly)
ggplotly(plot14)
```
