---
title: "DISCOVR SOT Cleaning and Analyzing"

output: html_document
---
#### Libraries
```{r message=FALSE}
library(readr)
library(dplyr)
library(ggplot2)
library(lubridate)
library(plotly)
```

#### Importing, formatting, and cleaning data from OpenEI DISCOVR page 
#### https://apps.openei.org/DISCOVR/#summaryTables

```{r message=FALSE, show_col_types = FALSE}
library(readr)
# Weather from August 26, 2019 through October 31, 2020
# Growth Data from August 26, 2019 through October 30, 2020
the_weather <- read.csv(file = "https://data.openei.org/files/5693/DISCOVR_SOT_weather_2020.csv")
the_data <- read_csv(file = "https://data.openei.org/files/5693/DISCOVR_SOT_cultivation-composition_2020.csv")
```

#### Transform Datetime into POSIXct for growth and weather data then strip time from weather DateTime and isolate only date in new column
```{r}
library(lubridate)
the_data$DateTime <- mdy_hm(the_data$DateTime, tz = "UTC")

library(lubridate)
library(dplyr)
the_weather$Date <- mdy_hm(the_weather$DATETIME, tz = "UTC")
the_weather <- the_weather %>%
  mutate(Date = as.Date(Date))
```

#### Isolate desired date range
```{r}
library(dplyr)
the_weather <- the_weather%>% 
  filter(Date >= as.Date('2020-06-01') & Date <= as.Date('2020-06-30'))

the_data <- the_data %>% 
  filter(DateTime >= as.Date('2020-06-01 00:00:00') & DateTime <= as.Date('2020-06-30 23:55:00'))
```

#### Isolate desired strain - however, there is only one strain in June, P.Celerei
```{r}
strain_weather<- the_weather[(the_weather$StrainID == "P.celeri"),]
strain_data <- the_data[(the_data$StrainID == "P.celeri"),]
strain_data <- strain_data[!(strain_data$PondID == "inoc"),]
```
#### Find daily par by finding 24 hour average, then find DLI by multiplying PAR by 24 hours in day and 0.0036 conversion factor. Scalings are done for graphing purposes
```{r}
library(dplyr)
PAR <- strain_weather %>%
  group_by(Date) %>%
  summarise(PPFD.umol.m2s = mean(HOBO.PAR))%>%
  rowwise(PPFD.umol.m2s) %>%
  mutate(DLI.mol.m2.day = (sum(PPFD.umol.m2s * 24 * 0.0036))) %>%
  mutate(DLI.scaled.hundreth = (sum(PPFD.umol.m2s * 24 * 0.0036 * .01))) %>%
  mutate(DLI.scaled.quarter = (sum(PPFD.umol.m2s * 24 * 0.0036 * 0.25)))
```

#### create long data frame for each variable
```{r}
strain_weather <- data.frame("DateTime" = PAR$Date, "Variable" = "DLI", "Value" = PAR$DLI.mol.m2.day, "PondID" = "DLI for all Ponds")
strain_weather_hundreth <- data.frame("DateTime" = PAR$Date, "Variable" = "DLI", "Value" = PAR$DLI.scaled.hundreth, "PondID" = "DLI for all Ponds") 
strain_weather_quarter <- data.frame("DateTime" = PAR$Date, "Variable" = "DLI", "Value" = PAR$DLI.scaled.quarter, "PondID" = "DLI for all Ponds")
strain_afdw <- data.frame("DateTime" = strain_data$DateTime, "Variable" = "AFDW.AVE", "Value" = strain_data$AFDW.AVE, "PondID" = strain_data$PondID)
strain_ahyp <- data.frame("DateTime" = strain_data$DateTime, "Variable" = "AHYP", "Value" = strain_data$AHYP.all.ponds, "PondID" = strain_data$PondID)
strain_nh4 <- data.frame("DateTime" = strain_data$DateTime, "Variable" = "NH4.AVE", "Value" = strain_data$NH4.AVE, "PondID" = strain_data$PondID)
strain_po4 <- data.frame("DateTime" = strain_data$DateTime, "Variable" = "PO4.AVE", "Value" = strain_data$PO4.AVE, "PondID" = strain_data$PondID)
strain_fame <- data.frame("DateTime" = strain_data$DateTime, "Variable" = "FAME", "Value" = strain_data$FAME, "PondID" = strain_data$PondID)
strain_carbs <- data.frame("DateTime" = strain_data$DateTime, "Variable" = "Carbohydrates", "Value" = strain_data$Carbohydrates, "PondID" = strain_data$PondID)
strain_protein <- data.frame("DateTime" = strain_data$DateTime, "Variable" = "Protein", "Value" = strain_data$Protein, "PondID" = strain_data$PondID)
```

#### Combine into one long form data frame
```{r}
all_variable <- rbind(strain_afdw, strain_ahyp, strain_fame, strain_nh4, strain_po4, strain_protein, strain_carbs, strain_weather) %>%
  na.omit((all_variable))
dli_afdw <- rbind(strain_afdw, strain_weather_hundreth) %>%
  na.omit((dli_afdw))
dli_ahyp <- rbind(strain_ahyp, strain_weather_quarter) %>%
  na.omit((dli_ahyp))
```


#### full thing

```{r}
library(ggplot2)
plot1 <- ggplot(all_variable) +
           aes(x = DateTime, y = Value, fill = Variable, colour = PondID) +
           geom_line(size = 0.5) +
           theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
           scale_fill_hue(direction = 1) +
           scale_color_hue(direction = 1) +
           labs(x = "DateTime", y = "Value", fill = "Variable", color = "PondID") +
           theme_minimal()
```

```{r, echo = FALSE, message=FALSE}
library(plotly)
ggplotly(plot1)

```


#### Facets by pond all black
```{r}
library(ggplot2)
plot2 <- ggplot(all_variable) +
           aes(x = DateTime, y = Value, fill = Variable) +
           geom_line(size = 0.5, colour = "#112446") +
           scale_fill_hue(direction = 1) +
           labs(x = "DateTime", y = "Value", fill = "Variable") +
           theme_minimal() +
           facet_wrap(vars(PondID))
```

```{r, echo = FALSE, message=FALSE}
library(plotly)
ggplotly(plot2)

```


```{r}
library(ggplot2)
### Facets by ponds, color = variable
plot3 <- ggplot(all_variable) +
           aes(x = DateTime, y = Value, colour = Variable) +
           geom_line(size = 0.5) +
           scale_color_hue(direction = 1) +
           labs(x = "DateTime", y = "Value", color = "PondID") +
           theme_minimal() +
           facet_wrap(vars(PondID))
```

```{r, echo = FALSE, message=FALSE}
library(plotly)
ggplotly(plot3)

```


#### Facets by variable, color = PondID
```{r}
library(ggplot2)
plot4 <- ggplot(all_variable) +
           aes(x = DateTime, y = Value, colour = PondID) +
           geom_line(size = 0.5) +
           scale_color_hue(direction = 1) +
           theme_minimal() +
           facet_wrap(vars(Variable), scales = "free")
```

```{r, echo = FALSE, message=FALSE}
library(plotly)
ggplotly(plot4)

```


#### AFDW vs Date with points and lines
```{r}
library(ggplot2)
plot5 <- ggplotly(ggplot(strain_afdw) +
           aes(x = DateTime, y = Value, colour = PondID) +
           geom_point(shape = "circle", size = 1.5) +
           geom_line() +
           scale_color_hue(direction = 1) +
           theme_minimal() +
           facet_wrap(vars(Variable)))
```

```{r, echo = FALSE, message=FALSE}
library(plotly)
ggplotly(plot5)

```


#### AFDW vs Date with lines only
```{r}
library(ggplot2)
plot6 <- ggplotly(ggplot(strain_afdw) +
           aes(x = DateTime, y = Value, colour = PondID) +
           geom_line(size = 0.5) +
           scale_color_hue(direction = 1) +
           theme_minimal() +
           facet_wrap(vars(Variable)))
```

```{r, echo = FALSE, message=FALSE}
library(plotly)
ggplotly(plot6)

```


#### AFDW with DLI
```{r}
library(ggplot2)
plot7 <- ggplotly(ggplot(dli_afdw) +
           aes(x = DateTime, y = Value, colour = PondID) +
           geom_point() +
           geom_line(size = 0.5) +
           scale_color_hue(direction = 1) +
           theme_minimal())
```

```{r, echo = FALSE, message=FALSE}
library(plotly)
ggplotly(plot7)

```


#### DLI with slope productivity (ahyp)
```{r}
library(ggplot2)
plot8 <- ggplotly(ggplot(dli_ahyp) +
  aes(x = DateTime, y = Value, colour = PondID) +
  geom_line(size = 0.5) +
  scale_color_hue(direction = 1) +
  theme_minimal())
```

```{r, echo = FALSE, message=FALSE}
library(plotly)
ggplotly(plot8)

```


#### AFDW vs Date facets by ponds
```{r}
library(ggplot2)
plot9 <- ggplotly(ggplot(strain_data) +
           aes(x = DateTime, y = AFDW.AVE, colour = PondID) +
           geom_line(size = 0.5) +
           scale_color_hue(direction = 1) +
           theme_minimal() +
           facet_wrap(vars(PondID)))
```
           
```{r, echo = FALSE, message=FALSE}
library(plotly)
ggplotly(plot9)

```
